Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-08-20 manuscript/main.tex
population consistency proof

% \definecolor{myblue}{RGB}{0, 0, 0}
% \newcommand{\blue}[1]{{\color{myblue}#1}}
\startlocaldefs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Uncomment next line to change            %%
%% the type of equation numbering           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\numberwithin{equation}{section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Axiom, Claim, Corollary, Hypothesis, %%
%% Lemma, Theorem, Proposition              %%
%% use \theoremstyle{plain}                 %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{plain}
\newtheorem{axiom}{Axiom}
\newtheorem{claim}[axiom]{Claim}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Assumption, Definition, Example,     %%
%% Notation, Property, Remark, Fact         %%
%% use \theoremstyle{definition}            %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{example}{Example}
\newtheorem*{fact}{Fact}
\newtheorem{remark}{Remark}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Please put your definitions here:        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\newcommand{\jongmin}[1]{
	{ \color{teal} \textit{(JM:) #1}}
}

@@

	\subsection{ Tucker's Criterion  }\label{section:sub:tucker} 
	    \jongmin{comment:maybe we can move this section to precede the algorithm section. then the new structure will introduce population version first and introduce finite-sample estimation procedure.}
	The fundamental property of classical scalar PLS is that the PLS component direction  corresponds to the first eigenvector of the squared covariance matrix, satisfying  the Tucker's Criterion \citep{Tucker1938}.
	Under a mild assumption,
	We derive an analogous result  in our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
	This justifies our estimation procedure introduced in Section \ref{section:main:our_algorithm}.
	We omit $l$ in the notations and first define the cross-covariance term between the response and the functional predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$): 
	\begin{equation}\label{def:cross_covariance_yx}
		\sigma_{YX}
		=
		\bigl(
		\sigma_{YX, 1}(t) , \ldots, \sigma_{YX, K}(t) 
		\bigr)
		:=
		\bigl(
		\mathbb{E}
		[Y_1 X_{11}]
		,\ldots, 
		\mathbb{E}
		[Y_1  X_{1K}]
		\bigr)   \in \mathcal{F}^{\otimes K},
	\end{equation}
	and between the response and the scalar predictor:
	\begin{equation*}
		\sigma_{YZ} 
		= 
		(\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top 
		:= 
		\bigl(
		\mathbb{E}[Y_1 Z_{11}]
		,\ldots,
		\mathbb{E}[Y_1 Z_{1p}]
		\bigr)^\top %= E(Y\mathbf{Z})
		\in \mathbb{R}^p.
	\end{equation*}
	Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
	\begin{equation*}
		\Sigma_{YW} :=  
		\mathbb{E}
		[ Y_1 W_1 ]
		=
		\bigl(
		\sigma_{YX, 1} , \ldots, \sigma_{YX, K} , \, \sigma_{YZ}
		\bigr) \in \mathbb{H}.
	\end{equation*}
	Based on these definitions, we introduce two cross-covariance operators and their properties.
	\begin{lemma}\label{lemma:cross_cov_functional}
		Define the operator $
		\mathcal{C}_{YW}
		=
		\mathbb{E}(W_1 \otimes_\mathbb{H} Y_1)
		: \mathbb{H} \rightarrow \mathbb{R}$ such that for any $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathbb{H}$, it maps $h$ to a real number as: \begin{equation*} \mathcal{C}_{YW} h := \mathbb{E} \left[ \langle W_1, h \rangle_\mathbb{H} Y_1 \right] = \langle \Sigma_{YW}, h \rangle_\mathbb{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt + \sigma_{YW}^\top \mathbf{v}. \end{equation*} 
		\jongmin{instead of showing $\mathcal{U}$ is compact, let's show $\mathcal{C}_{YW}$ is compact. This way, we don't need uniform continuiity of $\sigma_{YX}$.}If there exist finite constants $Q_1$ and $Q_2$ such that
		\begin{align}\label{condition_for_compact}
			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
		\end{align}
		the operator $\mathcal{C}_{YW}$ is a compact operator.
	\end{lemma}
	Proof of Lemma \ref{lemma:cross_cov_functional}
	is provided in Appendix \ref{section:proof:lemma:cross_cov_functional}.
	\begin{lemma}\label{lemma:cross_cov_operator}
		Define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathbb{H}$,
		which	maps  $d \in \mathbb{R}$ to a hybrid object in $\mathbb{H}$ as follows:
		%%%%
		\begin{align*}		
			\mathcal{C}_{WY} d 
			:= 
			\mathbb{E} 
			\bigl[
			\langle Y_1, d \rangle W_1 
			\bigr] 
			= 
			\mathbb{E}
			[ Y_1 W_1 d ] =  d \, \Sigma_{Y W}.
		\end{align*}
		Then	$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
	\end{lemma}

@@

	The following theorem introduces the population-level PLS and Tucker's Criterion, adapted to our scalar-on-hybrid regression model setting, based on the aforementioned operators defined in the hybrid space.
	\begin{theorem}[Tucker's criterion]\label{theorem:population_PLS} Under the conditions of Lemma \ref{lemma:cross_cov_functional}, the constrained maximum
		\begin{equation*} 
			\max \limits_{\substack{\xi \in \mathbb{H} \\ \Vert \xi \Vert_\mathbb{H}=1}} \operatorname{Cov}^2 \left(\langle W_1 , \, \xi \rangle_\mathbb{H}, Y_1 \right)
		\end{equation*} 
		is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
	\end{theorem}
	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.

@@

  \begin{theorem}[$L^2$ Convergence of Hybrid PLS] \label{thm:hybrid_pls_convergence} Let $Y_i$ be a scalar response and $W_i$ be a hybrid predictor in the hybrid Hilbert space $\mathbb{H} = (\mathbb{L}^2[0,1])^K \times \mathbb{R}^p$. Let $\hat{Y}_i = \langle \beta, W_i \rangle_{\mathbb{H}}$ denote the ordinary linear regression solution, where $\beta \in \mathbb{H}$ is the true regression coefficient. Let $\hat{Y}_{i,L} = \sum_{l=1}^L \hat{c}^{[l]} \rho_i^{[l]}$ be the Hybrid PLS approximation with $L$ components, where $\rho_i^{[l]} = \langle W_i, \xi^{[l]} \rangle_{\mathbb{H}}$ is the $l$-th PLS score and $\xi^{[l]} \in \mathbb{H}$ is the $l$-th PLS direction. Then, the Hybrid PLS approximation converges to the ordinary linear regression solution in the mean-squared ($L^2$) sense: $$ \lim_{L \to \infty} E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = 0 $$ \end{theorem} \begin{proof} The proof proceeds in three main steps: first, establishing that the PLS directions form a complete orthonormal system (CONS) for the relevant predictor subspace; second, expressing the ordinary linear regression solution as an infinite series in this PLS basis; and third, showing that the mean-squared error of the PLS approximation vanishes as the number of components increases. \subsection*{1. The PLS Directions Form a Complete Orthonormal System (CONS)} The Hybrid PLS algorithm iteratively constructs a set of directions $\{\xi^{[l]}\}_{l=1}^\infty$ from the predictors. The $l$-th PLS direction, $\xi^{[l]}$, is obtained as the principal eigenfunction of the operator $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$, where the superscript $[l]$ denotes that the operator is constructed from the residualized response $Y^{[l]}$ and predictors $W^{[l]}$ from the previous step. \paragraph{1.1 Orthonormality through Residualization} The iterative nature of the PLS algorithm guarantees the orthonormality of the directions. The \textbf{residualization (or orthogonalization)} step is crucial. After the $(l-1)$-th PLS direction $\xi^{[l-1]}$ is determined, the predictors and response are adjusted to remove the linear effect of this component. Specifically, for sample $i$: $$W_i^{[l]} = W_i^{[l-1]} - \langle W_i^{[l-1]}, \xi^{[l-1]} \rangle_{\mathbb{H}} \xi^{[l-1]}$$ $$Y_i^{[l]} = Y_i^{[l-1]} - \hat{c}^{[l-1]} \rho_i^{[l-1]}$$ where $W_i^{[1]} = W_i$ and $Y_i^{[1]} = Y_i$. This process ensures that the residualized predictors $W_i^{[l]}$ are orthogonal to all previous directions $\xi^{[j]}$ for $j < l$. Consequently, the newly found direction $\xi^{[l]}$, being derived from $W_i^{[l]}$, will be orthogonal to $\{\xi^{[1]}, \ldots, \xi^{[l-1]}\}$. By convention, PLS directions are normalized to have unit norm ($\Vert \xi^{[l]} \Vert_{\mathbb{H}} = 1$). Thus, the set $\{\xi^{[l]}\}_{l=1}^\infty$ is an orthonormal set. \paragraph{1.2 Completeness} The PLS algorithm, by repeatedly extracting the direction of maximum covariance from the residual space, exhaustively captures all linear information within the predictors that is correlated with the response. This iterative process terminates when the residualized predictors no longer exhibit covariance with the residualized response. Therefore, the span of the PLS directions, $\text{span}\{\xi^{[l]}\}_{l=1}^\infty$, precisely constitutes the subspace of $\mathbb{H}$ that contains all the linear information in the predictors relevant to predicting the response. This implies that $\{\xi^{[l]}\}_{l=1}^\infty$ forms a CONS for this relevant predictor subspace. \subsection*{2. The Ordinary Linear Regression Solution as a Series Expansion in the PLS Basis} Since $\{\xi^{[l]}\}_{l=1}^\infty$ is a CONS for the relevant predictor subspace, the true hybrid regression coefficient $\beta \in \mathbb{H}$ can be expressed as an infinite series in this basis: $$ \beta = \sum_{l=1}^{\infty} \langle \beta, \xi^{[l]} \rangle_{\mathbb{H}} \xi^{[l]} $$ Substituting this expansion into the definition of the ordinary linear regression solution $\hat{Y}_i$: $$ \hat{Y}_i = \langle \beta, W_i \rangle_{\mathbb{H}} = \left\langle \sum_{l=1}^{\infty} \langle \beta, \xi^{[l]} \rangle_{\mathbb{H}} \xi^{[l]}, W_i \right\rangle_{\mathbb{H}} $$ By the linearity of the inner product in a Hilbert space: $$ \hat{Y}_i = \sum_{l=1}^{\infty} \langle \beta, \xi^{[l]} \rangle_{\mathbb{H}} \langle \xi^{[l]}, W_i \rangle_{\mathbb{H}} $$ Let $c^{[l]} = \langle \beta, \xi^{[l]} \rangle_{\mathbb{H}}$ be the true coefficient for the $l$-th component and $\rho_i^{[l]} = \langle W_i, \xi^{[l]} \rangle_{\mathbb{H}}$ be the $l$-th PLS score for sample $i$. Then, $$ \hat{Y}_i = \sum_{l=1}^{\infty} c^{[l]} \rho_i^{[l]} $$ This shows that the exact regression solution is an infinite series involving the PLS scores. The PLS approximation $\hat{Y}_{i,L}$ is a partial sum of this series. Furthermore, it can be shown that the estimated coefficients $\hat{c}^{[l]}$ in the PLS approximation $\hat{Y}_{i,L}$ are consistent estimators of the true coefficients $c^{[l]}$. \subsection*{3. Proof of $L^2$ Convergence} Now, we examine the mean-squared error between the PLS approximation and the ordinary linear regression solution: $$ E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = E\left[ \left\| \sum_{l=1}^{L} c^{[l]} \rho_i^{[l]} - \sum_{l=1}^{\infty} c^{[l]} \rho_i^{[l]} \right\|^2 \right] $$ This can be rewritten as the expectation of the squared norm of the "tail" of the series: $$ E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = E\left[ \left\| - \sum_{l=L+1}^{\infty} c^{[l]} \rho_i^{[l]} \right\|^2 \right] $$ Since the PLS scores $\{\rho_i^{[l]}\}_{l=1}^\infty$ form an orthogonal system in the space of random variables (due to the orthogonality of $\{\xi^{[l]}\}$ and properties of expectation), the expectation of the squared sum simplifies to the sum of the expectations of the squared individual terms: $$ E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = \sum_{l=L+1}^{\infty} (c^{[l]})^2 E[(\rho_i^{[l]})^2] $$ The infinite series $\sum_{l=1}^{\infty} (c^{[l]})^2 E[(\rho_i^{[l]})^2]$ represents the total variance explained by the predictors and is a convergent series (related to the total variance of $\hat{Y}_i$). For any convergent series, the sum of its tail (i.e., from $L+1$ to infinity) must approach zero as $L$ tends to infinity. $$ \lim_{L \to \infty} \sum_{l=L+1}^{\infty} (c^{[l]})^2 E[(\rho_i^{[l]})^2] = 0 $$ Therefore, $$ \lim_{L \to \infty} E\left[ \| \hat{Y}_{i,L} - \hat{Y}_i \|_{L^2(\Omega)}^2 \right] = 0 $$ This concludes the proof that the Hybrid PLS approximation converges to the ordinary linear regression solution in the mean-squared sense. \end{proof}

@@

	\subsection{Proof of Theorem \ref{theorem:population_PLS}}\label{section:proof:theorem:population_PLS}
	\begin{proof}
		by Theorem 4.3.1 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
		since $\mathcal{C}_{YW}$ is compact by Lemma \ref{lemma:cross_cov_functional}, it 
		has the singular value decomposition of $\mathcal{C}_{YW}$, given by:
		\begin{equation*}
			\mathcal{C}_{YW} = \sum \limits_{j=1}^\infty \iota_j (f_{1j} \otimes f_{2j}).
		\end{equation*}
		Let $\Vert \cdot \Vert_{\mathrm{op}}$ denote an operator norm. By  4.3.4 in \citet{hsingTheoreticalFoundationsFunctional2015}, we have
		\begin{equation*}
			\Vert \mathcal{C}_{YW} \Vert_{\mathrm{op}} = \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | \mathcal{C}_{YW} h |^2 
			= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | E(\langle W, h \rangle_\mathbb{H} Y)|^2 
			= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} \textnormal{Cov}^2(\langle W, h \rangle_\mathbb{H}, Y) 
			= \kappa_1^2,
		\end{equation*}
		with maximum attained at $h=f_{11}$, which is an eigenfunction of  $\mathcal{C}_{YW}^* \, \circ \, \mathcal{C}_{YW} = \mathcal{C}_{WY} \, \circ \, \mathcal{C}_{YW} = \mathcal{U}$ corresponding to the largest eigenvalue $\kappa_1^2.$
		This completes the proof of Theorem \ref{theorem:population_PLS}.
	\end{proof}

>>>>

% \definecolor{myblue}{RGB}{0, 0, 0}
% \newcommand{\blue}[1]{{\color{myblue}#1}}
\startlocaldefs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Uncomment next line to change            %%
%% the type of equation numbering           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\numberwithin{equation}{section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Axiom, Claim, Corollary, Hypothesis, %%
%% Lemma, Theorem, Proposition              %%
%% use \theoremstyle{plain}                 %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{plain}
\newtheorem{axiom}{Axiom}
\newtheorem{claim}[axiom]{Claim}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}%custom
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Assumption, Definition, Example,     %%
%% Notation, Property, Remark, Fact         %%
%% use \theoremstyle{definition}            %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{example}{Example}
\newtheorem*{fact}{Fact}
\newtheorem{remark}{Remark}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Please put your definitions here:        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\newcommand{\jongmin}[1]{
	{ \color{teal} \textit{(JM:) #1}}
}

@@

	\subsection{ Tucker's Criterion  }\label{section:sub:tucker} 
	    \jongmin{comment:maybe we can move this section to precede the algorithm section. then the new structure will introduce population version first and introduce finite-sample estimation procedure.}
	The fundamental property of classical scalar PLS is that the PLS component direction  corresponds to the first eigenvector of the squared covariance matrix, satisfying  the Tucker's Criterion \citep{Tucker1938}.
	Under a mild assumption,
	We derive an analogous result  in our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
	This justifies our estimation procedure introduced in Section \ref{section:main:our_algorithm}.
For notational simplicity, we omit the index $l$. At the population level, where the random objects are fully observed, it suffices to consider $Y_1$ and $W_1$ rather than their sampled realizations.
We assume 
$\mathbb{E}[Y_1]=0 \in \mathbb{R}$ and $\mathbb{E}[W_1] = 0 \in \mathbb{H}$.
 We first define the cross-covariance between the response and the functional predictors, where the predictors correspond to the observed versions for $l=1$ and to the residualized versions for $l \ge 2$:
	\begin{equation}\label{def:cross_covariance_yx}
		\sigma_{YX}
		=
		\bigl(
		\sigma_{YX, 1}(t) , \ldots, \sigma_{YX, K}(t) 
		\bigr)
		:=
		\bigl(
		\mathbb{E}
		[Y_1 X_{11}]
		,\ldots, 
		\mathbb{E}
		[Y_1  X_{1K}]
		\bigr)   \in \mathcal{F}^{\otimes K},
	\end{equation}
	and between the response and the scalar predictor:
	\begin{equation*}
		\sigma_{YZ} 
		= 
		(\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top 
		:= 
		\bigl(
		\mathbb{E}[Y_1 Z_{11}]
		,\ldots,
		\mathbb{E}[Y_1 Z_{1p}]
		\bigr)^\top %= E(Y\mathbf{Z})
		\in \mathbb{R}^p.
	\end{equation*}
	Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
	\begin{equation*}
		\Sigma_{YW} :=  
		\mathbb{E}
		[ Y_1 W_1 ]
		=
		\bigl(
		\sigma_{YX, 1} , \ldots, \sigma_{YX, K} , \, \sigma_{YZ}
		\bigr) \in \mathbb{H}.
	\end{equation*}
	Based on these definitions, we introduce two cross-covariance operators and their properties.
	\begin{lemma}\label{lemma:cross_cov_functional}
		Define the operator $
		\mathcal{C}_{YW}
		=
		\mathbb{E}(W_1 \otimes_\mathbb{H} Y_1)
		: \mathbb{H} \rightarrow \mathbb{R}$ such that for any $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathbb{H}$, it maps $h$ to a real number as: \begin{equation*} \mathcal{C}_{YW} h := \mathbb{E} \left[ \langle W_1, h \rangle_\mathbb{H} Y_1 \right] = \langle \Sigma_{YW}, h \rangle_\mathbb{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt + \sigma_{YW}^\top \mathbf{v}. \end{equation*} 
		\jongmin{instead of showing $\mathcal{U}$ is compact, let's show $\mathcal{C}_{YW}$ is compact. This way, we don't need uniform continuiity of $\sigma_{YX}$.}If there exist finite constants $Q_1$ and $Q_2$ such that
		\begin{align}\label{condition_for_compact}
			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
		\end{align}
		the operator $\mathcal{C}_{YW}$ is a compact operator.
	\end{lemma}
	Proof of Lemma \ref{lemma:cross_cov_functional}
	is provided in Appendix \ref{section:proof:lemma:cross_cov_functional}.
	\begin{lemma}\label{lemma:cross_cov_operator}
		Define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathbb{H}$,
		which	maps  $d \in \mathbb{R}$ to a hybrid object in $\mathbb{H}$ as follows:
		%%%%
		\begin{align*}		
			\mathcal{C}_{WY} d 
			:= 
			\mathbb{E} 
			\bigl[
			\langle Y_1, d \rangle W_1 
			\bigr] 
			= 
			\mathbb{E}
			[ Y_1 W_1 d ] =  d \, \Sigma_{Y W}.
		\end{align*}
		Then	$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
	\end{lemma}

@@

	The following theorem introduces the population-level PLS and Tucker's Criterion, adapted to our scalar-on-hybrid regression model setting, based on the aforementioned operators defined in the hybrid space.
	\begin{theorem}[Tucker's criterion]\label{theorem:population_PLS} Under the conditions of Lemma \ref{lemma:cross_cov_functional}, the constrained maximum
		\begin{equation*} 
			\max \limits_{\substack{\xi \in \mathbb{H} \\ \Vert \xi \Vert_\mathbb{H}=1}} \operatorname{Cov}^2 \left(\langle W_1 , \, \xi \rangle_\mathbb{H}, Y_1 \right)
		\end{equation*} 
		is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
	\end{theorem}
	Note that the maximizer is a deterministic element of $\mathbb{H}$.
	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.

@@

\jongmin{comment: I added the following properties, motivated by Proposition 4 of \citet{predaPLSRegressionStochastic2005} and section 2 of \citet{aguileraPenalizedVersionsFunctional2016}. }

\begin{lemma} \label{lem:regression_W_rho} The population-level least square regression coefficient of regressing $W_1^{[l]}$ on its score $\rho_1^{[l]} = \langle W_1^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}}$ is $\mathbf{\xi^{[l]}} \in \mathbb{H}$. This coefficient is used in the residualization process as follows: \begin{align*} W_1^{[l]} &= W_1^{[l-1]} - \langle W_1^{[l-1]}, \xi^{[l-1]} \rangle_{\mathbb{H}} \xi^{[l-1]},\end{align*} where  $W_1^{[1]} = W_1$. \end{lemma} 
Proof of Lemma \ref{lem:regression_W_rho} is provided in Appendix \ref{section:proof:lem:regression_W_rho}.

 We define an operator $\mathcal{T}$ that maps an element $g \in \mathbb{H}$   (representing a potential regression coefficient) to the predicted response.
\begin{lemma}\label{lemma:tau_ast}
	Define the linear operator $\mathcal{T}: \mathbb{H} \to \mathbb{R}$ that maps  $g \in \mathbb{H}$ to 
	$
	\mathcal{T}g = \langle W, g \rangle_{\mathbb{H}}
	$.
 Let $\mathcal{T}^\ast: \mathbb{R} \to \mathbb{H}$ denote its adjoint operator. Then,
	\[
	\Sigma_{YW}^{[1]} = \mathcal{T}^\ast Y.
	\]
\end{lemma}
Proof of Lemma \ref{lemma:tau_ast} is provided in Appendix \ref{section:rpoof:lemma:tau_ast}.

\begin{proposition}\label{proposition:pls_direction_in_range_T_ast}
	All PLS Directions Reside in $R(\mathcal{T}^\ast  )$
\end{proposition}
 Proof of Proposition \ref{proposition:pls_direction_in_range_T_ast} is provided in Appendix \ref{section:proof:proposition:pls_direction_in_range_T_ast}

\begin{proposition}
	\label{proposition:CONS}
	The set of PLS directions $\{\xi^{[l]}\}_{l=1}^\infty$ forms a complete orthonormal system (CONS) for $R(\mathcal{T}^*)$.
\end{proposition}
Proof of Proposition \ref{proposition:CONS}
is provided in Appendix \ref{section:proof:proposition:CONS}.

\begin{corollary}
	\label{cor:orthogonal_scores}
	Given that $\{\xi^{[l]}\}_{l=1}^\infty$ is a complete orthonormal system (CONS) for $R(\mathcal{T}^*)$, the corresponding PLS scores $\rho^{[l]}$ can be equivalently expressed as $\rho^{[l]} = \langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}} = \langle W, \xi^{[l]} \rangle_{\mathbb{H}}$. Furthermore, the set of PLS scores $\{\rho^{[l]}\}_{l=1}^\infty$ forms an orthogonal system, that is, for any $j \neq l$, $\mathbb{E}[\rho^{[j]} \rho^{[l]}] = 0$.
\end{corollary}
Let $\beta_{\mathrm{OLS}}$ denote a minimizer of  the mean squared error $ \mathbb{E}[\|Y - \langle \beta, W \rangle_{\mathbb{H}}\|_2^2]$. It
satisfies the normal equation
\begin{equation}\label{normal_equation}
	\mathbb{E}[(Y - \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}})W] = 0 \in \mathbb{H}.
\end{equation}
If the operator $\mathcal{T}^\ast \mathcal{T}$ is invertible,  the minimizer is uniquely determined as 
$\beta_{\mathrm{OLS}} = (\mathcal{T}^\ast \mathcal{T})^{-1} \mathcal{T}^\ast Y$.
\begin{proposition}\label{proposition:nu_l}
	At the $l$-th iteration, the 
	population level least square regression coefficient of the residual response $Y^{[l]}$ on the score $\rho^{[l]}$ is defined as:
	$$\nu^{[l]} = \langle \beta_{\mathrm{OLS}}, \xi^{[l]} \rangle_{\mathbb{H}}.$$
\end{proposition}
Proof of Proposition \ref{proposition:nu_l} is provided in Appendix \ref{section:proof:proposition:nu_l}.

The following theorem states that the fitted values from hybrid PLS converge to those of ordinary linear regression in the mean-squared sense. This shows that hybrid PLS, as a dimension-reduction technique, can effectively capture the predictive power of a full linear model when a sufficient number of components is used.
\begin{theorem}[$L^2$ Convergence of Hybrid PLS at Population Level]\label{thm:hybrid_pls_convergence}
	 Define $Y_{\mathrm{OLS}} = \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}}$ as the population-level ordinary linear regression fitted value. Let $Y_{\mathrm{PLS}, L} = \sum_{l=1}^L \nu^{[l]} \rho^{[l]}$ be the Hybrid PLS fitted value with $L$ components. Then, the Hybrid PLS fitted value converges to the ordinary linear regression fitted value in the mean-squared sense:
	\begin{equation*}
		\lim_{L \to \infty} \mathbb{E}\left[ \| Y_{\mathrm{PLS},L } - Y_{\mathrm{OLS}} \|_2^2 \right] = 0
	\end{equation*}
\end{theorem}
 The proof of Theorem \ref{thm:hybrid_pls_convergence} is provided in Appendix \ref{section:proof:thm:hybrid_pls_convergence}.

@@

	\subsection{Proof of Theorem \ref{theorem:population_PLS}}\label{section:proof:theorem:population_PLS}
	\begin{proof}
		by Theorem 4.3.1 of \citet{hsingTheoreticalFoundationsFunctional2015}, 
		since $\mathcal{C}_{YW}$ is compact by Lemma \ref{lemma:cross_cov_functional}, it 
		has the singular value decomposition of $\mathcal{C}_{YW}$, given by:
		\begin{equation*}
			\mathcal{C}_{YW} = \sum \limits_{j=1}^\infty \iota_j (f_{1j} \otimes f_{2j}).
		\end{equation*}
		Let $\Vert \cdot \Vert_{\mathrm{op}}$ denote an operator norm. By  4.3.4 in \citet{hsingTheoreticalFoundationsFunctional2015}, we have
		\begin{equation*}
			\Vert \mathcal{C}_{YW} \Vert_{\mathrm{op}} = \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | \mathcal{C}_{YW} h |^2 
			= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} | \mathbb{E}(\langle W, h \rangle_\mathbb{H} Y)|^2 
			= \sup_{\substack{h \in \mathbb{H} \\ \Vert h \Vert_\mathbb{H}=1}} \textnormal{Cov}^2(\langle W, h \rangle_\mathbb{H}, Y) 
			= \kappa_1^2,
		\end{equation*}
		with maximum attained at $h=f_{11}$, which is an eigenfunction of  $\mathcal{C}_{YW}^* \, \circ \, \mathcal{C}_{YW} = \mathcal{C}_{WY} \, \circ \, \mathcal{C}_{YW} = \mathcal{U}$ corresponding to the largest eigenvalue $\kappa_1^2.$
		This completes the proof of Theorem \ref{theorem:population_PLS}.
	\end{proof}
